---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# semscholar: interfacing Semantic Scholar search engine with R

<!-- badges: start -->
<!-- badges: end -->

This web client wraps the Semantic Scholar RESTful API. 
[Semantic Scholar](https://www.semanticscholar.org/) is a free, 
nonprofit, academic search engine from the 
[Allen Institute for AI](https://allenai.org/). 

The client supports search for author profiles and mined metadata 
of scholarly works including citations, references and topics.
    
API Docs: <https://api.semanticscholar.org/>

## Installation

You can install the develpment version of semscholar from GitHub:

``` r
remotes::install_github("njahn82/semscholar")
```

## Paper Lookup

```{r}
library(semscholar)
s2_papers(
  c("10.1093/nar/gkr1047", 
             "14a22b032524573d15593abed170f9f76359e581", 
             "10.7717/peerj.2323", 
             "arXiv:0711.0914")
  )
```

Authors

```{r}
s2_papers("14a22b032524573d15593abed170f9f76359e581")$authors
```

Citations

```{r}
s2_papers("14a22b032524573d15593abed170f9f76359e581")$citations
```

References

```{r}
s2_papers("14a22b032524573d15593abed170f9f76359e581")$references
```

Topics

```{r}
s2_papers("14a22b032524573d15593abed170f9f76359e581")$topics
```
